\thesistitle

### 2019-07-29 sections/clonerefactor.tex
Fixed some issues with the formulas

\begin{equation}\label{eq:crtype3r}
\forall (c_1 \in S) \exists (c_2 \in S) x \neq y \land isType3R(c_1, c_2)
\end{equation}

Where \textit{S} is the set of all found clone classes. \textit{$\text{isType3R}(C_1, C_2)$} is a Boolean-valued function that denotes whether two clone classes are type 3R clones of each other. Two clone classes are type 3R clones of each other if each of their instances are within a certain distance of each other:

\begin{equation}\label{eq:istype3r}
\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land gap(i_1, i_2) < gap\_threshold
\end{equation}

Where \textit{F} is the file in which the clone instance is located. \textit{gap\_threshold} is the defined threshold percentage of the maximum gap size between two clone instances. \textit{$\text{gap}(I_1, I_2)$} is the function that calculates the gap between two clone instances. This gap is calculated by dividing the amount of statements in the gap by the amount of statements that both clone instances span together:

@@

\begin{equation}\label{eq:rangetotalorder}
R_1 < R_2 \text{ iff } end_line(R_1) < begin_line(R_2) \lor (end_line(R_1) = begin_line(R_2) \land end_column(R_1) < begin_column(R_2))
\end{equation}
\begin{equation}\label{eq:rangetotalorder2}
R_1 > R_2 \text{ iff } begin_line(R_1) > end_line(R_2) \lor (begin_line(R_1) = end_line(R_2) \land begin_column(R_1) > end_column(R_2))
\end{equation}

>>>>

\begin{equation}\label{eq:crtype3r}
\forall (c_1 \in S) \text{ }\exists (c_2 \in S)\text{ }x \neq y \land isType3R(c_1, c_2)
\end{equation}

Where \textit{S} is the set of all found clone classes. $\text{isType3R}(C_1, C_2)$ is a Boolean-valued function that returns whether two clone classes are type 3R clones of each other. Two clone classes are type 3R clones of each other if each of their instances are within a certain distance of each other:

\begin{equation}\label{eq:istype3r}
\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1)\text{ } \exists (i_2 \in C_2)\text{ } Fi_1 = Fi_2 \land gap(i_1, i_2) < gap\_threshold
\end{equation}

Where \textit{F} is the file in which the clone instance is located. \textit{gap\_threshold} is the defined threshold percentage of the maximum gap size between two clone instances. $\text{gap}(I_1, I_2)$ is the function that calculates the gap between two clone instances. This gap is calculated by dividing the amount of statements in the gap by the amount of statements that both clone instances span together:

@@

\begin{equation}\label{eq:rangetotalorder}
R_1 < R_2 \text{ iff } end\_line(R_1) < begin\_line(R_2) \lor (end\_line(R_1) = begin\_line(R_2) \land end\_column(R_1) < begin\_column(R_2))
\end{equation}
\begin{equation}\label{eq:rangetotalorder2}
R_1 > R_2 \text{ iff } begin\_line(R_1) > end\_line(R_2) \lor (begin\_line(R_1) = end\_line(R_2) \land begin\_column(R_1) > end\_column(R_2))
\end{equation}
